The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-30 document/ms.tex
words about likelihood function

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}

@@

We consider the following mean models and this list provides a qualitative
justification for each model:
\begin{itemize}
{\item \modelname{transit} -- a limb-darkened, exposure time integrated
transit light curve,}
{\item \modelname{variability} -- a pure Gaussian Process model to capture
stellar variability,}
{\item \modelname{outlier} -- a single outlier to account for a bad data
point,}
{\item \modelname{step} -- a step function to describe sudden pixel
sensitivity dropouts (SPSDs; \dfmtodo{CITE}), and}
{\item \modelname{box} -- a box to catch signals that are well fit by the
search scalar but insufficiently transit-like to be convincing.}
\end{itemize}
The functional forms of these models are given in \app{model-details}.

@@

>>>>

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}

@@

We consider the following mean models and this list provides a qualitative
justification for each model:
\begin{itemize}
{\item \modelname{transit} -- a limb-darkened, exposure time integrated
transit light curve,}
{\item \modelname{variability} -- a pure Gaussian Process model to capture
stellar variability,}
{\item \modelname{outlier} -- a single outlier to account for a bad data
point,}
{\item \modelname{step} -- a step function to describe sudden pixel
sensitivity dropouts \citep[SPSDs; for example][]{Christiansen:2013}, and}
{\item \modelname{box} -- a box to catch signals that are well fit by the
search scalar but insufficiently transit-like to be convincing.}
\end{itemize}
The functional forms of these models are given in \app{model-details}.

@@

In the following paragraphs, we describe the components of the probabilistic
model.
To perform parameter estimation under this model, we use the Markov Chain
Monte Carlo (MCMC) package \emcee\footnote{\url{http://dfm.io/emcee}}
\citep{Foreman-Mackey:2013} with an ensemble of 40 walkers.
We run each chain until the.

\paragraph{Priors}

For each candidate in our sample, we take the constraints on the stellar
parameters from the \kepler\ stellar properties catalog\footnote{The
\textsf{q1\_q17\_dr24\_stellar} table from the NASA Exoplanet Archive
\citep{Huber:2014}} and assume an empirical beta function prior on the
eccentricities based on the observed eccentricity distribution of long-period
planets discovered using radial velocities \citep{Kipping:2013}.
Table~\ref{tab:parameters} lists all the fit parameters and their prior
distributions.
Besides these listed priors, we add the extra constraint that no other
transits can occur in the baseline of the \kepler\ observations.
This constraint is overly conservative because there is some probability that
a second transit could occur in a data gap but we find that, in practice, most
of the posterior mass is at longer periods and the period inferences are not
significantly affected.

\paragraph{Likelihood function}

As above, we model the light curve as GP with a physical transit model as the
mean and a covariance matrix described by a Mat\'ern-3/2 kernel function.
The full likelihood function and some details of GP regression are given in
\app{gp-regression}.
For computational efficiency, we first perform a joint optimization of the
orbital parameters and GP hyperparameters to find the maximum \foreign{a
posteriori} model then keep these.
